Implementing Real-time Transport Services over an Ossified Network

### 2016-05-15 paper.tex
First complete draft of the Introduction

In practice, the only protocols that can be widely used in the Internet are
TCP and UDP. Other protocols are blocked by firewalls and other middleboxes.  
TCP provides sophisticated congestion control, coupled with a reliable,
ordered, byte stream API. These are suitable for many applications, but are
not necessarily appropriate for real-time traffic.  UDP exposes essentially
the raw IP packet delivery service, offering flexibility to develop new
protocols, but at the cost of requiring completely new protocol mechanisms
to be defined. While both protocols are usable for real-time applications,
neither really provides the right services and API.

@@

In this paper we develop an appropriate set of transport services and APIs
for real-time applications.
Then, we demonstrate that it is possible to realise these services and APIs
in the context of both TCP and UDP, despite the limitations imposed by the
legacy protocols, middleboxes, and ossification of the network. 
We present initial results to show that, despite the observed ossification,
the network has the flexibility to deploy new transport protocols, if care
is taken to reinterpret layer boundaries and deploy those new transports in
the context of TCP and UDP.

@@

Our contributions are ...
A discussion of the needs of real-time applications, and the appropriate
transport services and APIs to support those needs.
An outline of how those transport services can be realised over in the
context of UDP and TCP.
Preliminary deployments results, to show that there is the possibility
that these services are usable in the public Internet.

@@

We structure the remainder of this paper as follows.

%==================================================================================================
\section{Real-time Transport Services}

@@

%==================================================================================================
\section{Innovation and Ossification}

@@

%==================================================================================================
\section{Partial Reliability and TCP}

@@

%==================================================================================================
\section{Realising Transport Services}

@@

%==================================================================================================
\section{Related Work}

@@

%==================================================================================================
\section{Conclusions}

>>>>

In practice, the only protocols that can be widely used in the Internet are
TCP and UDP. Other protocols are blocked by firewalls and other middleboxes.  
TCP provides sophisticated congestion control, coupled with a reliable,
ordered, byte stream API. These are suitable for many applications, but are
not necessarily appropriate for real-time traffic.  UDP exposes the best-effort 
IP packet delivery service, offering flexibility to develop new protocols,
but at the cost of requiring completely new protocol mechanisms to be
defined. Both protocols are usable for real-time applications, but neither
really provides the right services and API.  This forces each application
to re-invent mechanisms that should be provided by the transport, increasing 
costs and complexity, raising barriers to innovation.

@@

In this paper we discuss the appropriate set of transport services and APIs
for real-time applications.
We demonstrate that it is possible to realise these services and APIs
in the context of both TCP and UDP, despite the limitations imposed by the
legacy protocols, middleboxes, and ossification of the network. 
We present initial results to show that, despite the observed ossification,
the network has the flexibility to deploy new transport protocols, if care
is taken to reinterpret layer boundaries and deploy those new transports in
the context of TCP and UDP.

@@

Our contributions are to identify the needs of real-time applications, and
the appropriate transport services and APIs to support those needs; 
to illustrate how those transport services can be realised on the current
Internet, in the context of UDP and TCP deployments; and 
to present some initial measurement results to show that the mechanisms we
propose ought to be usable in the public Internet.

@@

We begin, in Section \ref{sec:services} by discussing transport services 
for real-time applications, and outlining the common conceptual API that
those applications use. 
This is followed, in Section \ref{sec:ossification}, by a review of the
deployment considerations for new protocols, caused by ossification of
the network, with Section \ref{sec:partial} considering, in particular, how
TCP reliability semantics can evolve within the constraints of the deployed
infrastructure.
Section \ref{sec:realising} outlines how the transport services we have
identified can be realised in practical networks.
Finally, Section \ref{sec:related} discusses related work, and Section
\ref{sec:conclusions} concludes.

%==================================================================================================
\section{Real-time Transport Services}
\label{sec:services}

@@

%==================================================================================================
\section{Innovation and Ossification}
\label{sec:ossification}

@@

%==================================================================================================
\section{Partial Reliability and TCP}
\label{sec:partial}

@@

%==================================================================================================
\section{Realising Transport Services}
\label{sec:realising}

@@

%==================================================================================================
\section{Related Work}
\label{sec:related}

@@

%==================================================================================================
\section{Conclusions}
\label{sec:conclusions}
